---
title: "Statistics Resources"
---

### Textbooks

Theory: [*Mathematical Statistics, Old School* by John I. Marden](https://www.amazon.com/Mathematical-Statistics-John-I-Marden/dp/1542439604/ref=sr_1_1?ie=UTF8&qid=1547446031&sr=8-1&keywords=mathematical+statistics+old+school)   
*Textbook used for STAT 510 at the University of Illinois*
  
Machine Learning Methods (Graduate): [*The Elements of Statistical Learning* by Hastie, Tibshirani, and Friedman](https://www.amazon.com/Elements-Statistical-Learning-Prediction-Statistics/dp/0387848576/ref=sr_1_fkmr0_2?ie=UTF8&qid=1547446126&sr=8-2-fkmr0&keywords=esl+tibshirani)  
*Textbook used for STAT 542 at the University of Illinois*
  
Machine Learning Methods (Undergraduate): [*An Introduction to Statistical Learning* by James, Witten, Hastie, and Tibshirani](https://www.amazon.com/Introduction-Statistical-Learning-Applications-Statistics/dp/1461471370/ref=sr_1_fkmr0_1?ie=UTF8&qid=1547446126&sr=8-1-fkmr0&keywords=esl+tibshirani)  
*Textbook used for STAT 432 at the University of Illinois*
  
Deep Learning (Neural Networks): [*Deep Learning with R* by Chollet and Allaire](https://www.amazon.com/Deep-Learning-R-Francois-Chollet/dp/161729554X/ref=sr_1_3?ie=UTF8&qid=1547446307&sr=8-3&keywords=deep+learning+with+r)   
*Textbook used for STAT 430: Machine Learning for Financial Data at the University of Illinois*



### R Resources

[R Studio Cheatsheets](https://www.rstudio.com/resources/cheatsheets/)
  
[*R for Data Science* by Hadley Wickham and Garrett Grolemund](https://r4ds.had.co.nz/)
  
[Tidyverse](https://www.tidyverse.org/)

Hadley Wickham Book
ggplot2 guide
shiny guide
R Cheatsheets

### SAS Resources

[SAS User's Guide for High-Performance Procedures](https://support.sas.com/documentation/cdl/en/stathpug/68163/PDF/default/stathpug.pdf)
  
[A Comparison of HP and Legacy Procedures](https://support.sas.com/resources/papers/proceedings16/11670-2016.pdf)
  
[SAS Enterprise Miner 14.1 High-Performance Procedures](https://support.sas.com/documentation/onlinedoc/miner/em14/emhpprcref.pdf)
  
[SAS 9.3 ODS Graphics Designer User's Guide](https://support.sas.com/documentation/cdl/en/grstatdesignug/63226/PDF/default/grstatdesignug.pdf)
  
[SAS Studio 5.1 User's Guide](http://documentation.sas.com/api/docsets/webeditorug/5.1/content/webeditorug.pdf?locale=en)
  
### GitHub Resources

See Starred repositories

TO-DO: Add PDFs to resume, cv, data science certificate, other awards (if I can find them).  Add more links to study abroad work or econ awards. Add former affiliations (Econ Ambassadors and DFA)

```{r}
summary(mtcars$mpg)
```

```{r}
# ggplot(mtcars, aes(cyl)) + geom_bar()
```




